\documentclass[11pt]{article}

\usepackage{times}
\usepackage[english]{babel}

% -----------------------------------------------
% especially use this for you code
% -----------------------------------------------

\usepackage{courier}
\usepackage{listings}
\usepackage{color}
\usepackage{tabularx}
\usepackage{graphicx}

\definecolor{Gray}{gray}{0.95}

\definecolor{mygreen}{rgb}{0,0.6,0}
\definecolor{mygray}{rgb}{0.5,0.5,0.5}
\definecolor{mymauve}{rgb}{0.58,0,0.82}

\lstset{language=C++,
	basicstyle = \normalsize\ttfamily,   % the size and fonts that are used
	tabsize = 2,                    % sets default tabsize
	breaklines = true,              % sets automatic line breaking
	keywordstyle=\color{blue}\ttfamily,
	stringstyle=\color{red}\ttfamily,
	commentstyle=\color{mygreen}\ttfamily,
	numbers=left,
	keepspaces=true,
	showspaces=false,
	showstringspaces=false,
}

\begin{document}

\title{Programming in C/C++ \\
       Exercises set five: grammatical parsers
}
\date{\today}
\author{Christiaan Steenkist \\
Jaime Betancor Valado \\
Remco Bos \\
}

\maketitle
\section*{Exercise 30, calculator}
We got a calculator grammar.

\subsection*{Code listings}
\lstinputlisting[caption = grammar.gr]{src/a30/grammar.gr}

\section*{Exercise 31, conflicts}
We fixed numerous conflicts.

\subsection*{First grammar}
The first revision of the grammar solves the reduce/reduce conflicts that are caused by the \texttt{NUMBER} branches in the \texttt{expr} and \texttt{number} nonterminals. To solve this we removed the \texttt{expr} case because it is already represented in \texttt{number}.

\begin{lstlisting}
%token NUMBER

%%

expr:
    number
|
    expr '+' expr
|
    expr '-' expr
|
	// empty
;

number:
    NUMBER
;
\end{lstlisting}

\subsection*{Second grammar}
In this grammar we also solved the shift/reduce conflicts which were caused because '+' and '-' have equal priority and no explicitly specified resolution for these types of conflicts. We set them to equal priority but reduce and not shift as is customary with these operators.

\begin{lstlisting}
%token NUMBER

%left '+' '-'

%%

expr:
    number
|
    expr '+' expr
|
    expr '-' expr
|
	// empty
;

number:
    NUMBER
;
\end{lstlisting}

\section*{Exercise 32, priorities}
We added a new priority to a grammar.

\subsection*{Code listings}
\lstinputlisting[caption = grammar.gr]{src/a32/grammar.gr}

\section*{Exercise 35, separated lists}
We fixed the list grammar so it does what we want it to.

\subsection*{Design}
To accomodate multiple datatypes we use listtokens instead of WORDs.
To allow empty lists, lists can exist out of nothing (empty OR).
Because a list with one item can't be distinguished as a separated list we just count it as a normal list.
A separated list is thus counted as \texttt{[listtoken ',' listtoken]} with optional repetition of \texttt{[listtoken ',']}.
We abbreviated these nonterminals as \texttt{sepstart} and \texttt{sepend}.
To simplify some more we defined \texttt{[listtoken ',']} as \texttt{septoken}.

\subsection*{Code listings}
\lstinputlisting[caption = grammar.gr]{src/a35/grammar.gr}

\end{document}